---
title: "econ&mental"
author: Chenhao Huang
format: html
editor: visual
---

## Import Libraries

```{r}
library(ggplot2)
library(tidyverse)
library(lubridate)
library(RedditExtractoR)
library(httr)
library(zoo)
library(dplyr)
library(stringr)
library(wordnet)
```

## Load all the data in CSV files

```{r}
GDP <- read.csv("data/GDP.CSV") #GDP
PCE <- read.csv("data/PCE.csv") #Personal Consumption Expenditure
PI <- read.csv("data/PI.csv") #Personal Income
PSR <- read.csv("data/PSAVERT.csv") #Personal Savings Rate
UNRATE <- read.csv("data/UNRATE.csv") #Unemployment Rate
patient <- read.csv("data/Patient.csv") #number of adults seeking therapy
ment_trend <- read.csv("data/ment_trend.csv", skip = 2) #mental health trend on Google
calm <- read.csv("data/calm_downloads.csv") #calm downloads
```

## Convert the data into the correct type

```{r}
#| warning: false
#| error: false
patient$Year <- as.Date(paste0(patient$Year, "-01-01"))
GDP$DATE <- as.Date(GDP$DATE)
PCE$DATE <- as.Date(PCE$DATE)
PI$DATE <- as.Date(PI$DATE)
PSR$DATE <- as.Date(PSR$DATE)
UNRATE$DATE <- as.Date(UNRATE$DATE)
ment_trend$Month <- as.Date(paste0(ment_trend$Month, "-01"))
calm$Quarter <- as.Date(as.yearqtr(calm$Quarter, format = "%Y Q%q"))
```

## Get social media sentiment

First, get the posts from reddit

```{r}
subreddit <- "mentalhealth"
thread_urls <- find_thread_urls(subreddit = subreddit, sort_by = "hot")
threads <- thread_urls %>% select(date_utc, title)

threads
```

```{r}
sampled_indices <- sample(nrow(threads), 900)
sampled_threads <- threads[sampled_indices, ]
sampled_threads
```

Second, get sentiment. 0 is negative, 10 is positive

```{r}


# Define the get_sentiment function
get_sentiment <- function(prompt) {
    url <- "https://api.openai.com/v1/chat/completions"
    body <- list(
        model = "gpt-4",
        messages = list(
            list(
                role = "system",
                content = "You are a helpful assistant."
            ),
            list(
                role = "user",
                content = paste0("give me a one-word summary of the issue and sentiment from 0 (negative) to 10 (positive) for the following statement: ", prompt, ". Respond in this format: Issue, sentiment score.")
            )
        ),
        max_tokens = 1000
    )

    response <- POST(
        url,
        add_headers(`Authorization` = paste("Bearer", OPENAI_API_KEY),
                    `Content-Type` = "application/json"),
        body = body,
        encode = "json"
    )
    content <- content(response, "parsed")

    # Return the text of the response
    if (!is.null(content$choices) && length(content$choices) > 0 && !is.null(content$choices[[1]]$message)) {
        return(content$choices[[1]]$message$content)
    } else {
        return(NULL)  # or handle error appropriately
    }
}

# Example usage
text <- get_sentiment("Should I try to get a prescription for medical marijuana?")


issue <- sub("\n*(.*?),.*$", "\\1", text)
sentiment <- as.numeric(gsub("[^0-9]", "", text))

print(text)
print(issue)
print(sentiment)
```

```{r}
Issues <- c()
Sentiments <- c()

for (title in sampled_threads$title) {
  ai_response <- get_sentiment(title)
  issue <- sub("\n*(.*?),.*$", "\\1", ai_response)
  sentiment <- gsub("[^0-9]", "", ai_response)
  Issues <- c(Issues, issue)
  Sentiments <-  c(Sentiments, sentiment)
}

#clean it up a bit
Issues <- sapply(Issues, function(x) gsub("\n", "", x))

#update the dataframe
sampled_threads$Issues <- rep(NA, nrow(sampled_threads))
sampled_threads$Issues[1:898] <- Issues
sampled_threads$Sentiments <- rep(NA, nrow(sampled_threads))
sampled_threads$Sentiments[1:898] <- Sentiments

sampled_threads

```

## Visualize

Now we have all the data, let's take a look.

However, before we can do anything, we need to consider this: some data has different time frame. To solve this, when we compare two variables with different time frames, we can round the most specific data to the less specific data. For example, patient uses year, and GDP uses quarters. We take the average of the 4 quarters GDP to find a value for that year so it can be matched with the patient data.

```{r}
compute_analysis <- function(x, y) {
    # Check if the lengths of the vectors are the same
    if(length(x) != length(y)) {
        stop("The lengths of the vectors must be the same")
    }

    # Linear regression model
    model <- lm(y ~ x)

    # 95% Confidence Interval for the slope
    conf_interval <- confint(model, "x", level = 0.95)

    # Summary of the model to get p-value for slope
    model_summary <- summary(model)
    slope_p_value <- coef(model_summary)["x", "Pr(>|t|)"]

    # Testing the significance of the slope
    significant <- slope_p_value < 0.05

    # Results
    list(
        confidence_interval = conf_interval,
        p_value = slope_p_value,
        is_significant = significant
    )
}
```

## Let's take a look at all the correlations (econ vs mental health)

GDP vs Number of adults seeking therapy

```{r}
#look at GDP data
GDP
```

```{r}
#look at patient data
patient
```

```{r}
GDP <- GDP |> 
  rename(Year = DATE)
GDP$Year <- format(as.Date(GDP$Year), "%Y")
patient$Year <- format(as.Date(patient$Year), "%Y")

yearly_avg_gdp <- aggregate(GDP ~ Year, data = GDP, FUN = mean)


combined_data <- merge(patient, yearly_avg_gdp, by = "Year", all.x = TRUE)
combined_data <- head(combined_data, -1)
combined_data
```

```{r}
long_data <- tidyr::pivot_longer(combined_data, cols = c(patient_in_mil, GDP), names_to = "Variable", values_to = "Value")

ggplot(long_data, aes(x = Year, y = Value, color = Variable, group = Variable)) +
  geom_line() +
  geom_point() +
  theme_minimal() +
  labs(x = "Year", y = "Value", color = "Variable", title = "Patients and GDP over Years")


```

```{r}
ggplot(combined_data, aes(x = GDP, y = patient_in_mil)) +
  geom_point() +
  geom_smooth(method = "lm", color = "blue", se = FALSE)+
  theme_minimal() +
  labs(x = "GDP", y = "patient_in_mil", title = "Patients vs GDP")
```

```{r}
model <- lm(GDP ~ patient_in_mil, data = combined_data)
print(summary(model))
print(cor(combined_data$GDP, combined_data$patient_in_mil))
```

```{r}
compute_analysis(combined_data$GDP, combined_data$patient_in_mil)
```

Turns out there is a positive correlation! The higher the GDP, the more adults tend to get mental therapy.

GDP vs mental health trend on Google

```{r}
#need to reload the data because we tidied it to suit for other things
GDP <- read.csv("data/GDP.CSV")
GDP$DATE <- as.Date(GDP$DATE)
GDP
```

```{r}
ment_trend
```

```{r}
ment_trend <- ment_trend |> 
  rename(Quarter = Month)

GDP <- GDP |>
  rename(Quarter = DATE)

ment_trend$Quarter <- as.yearqtr(ment_trend$Quarter, format = "%Y-%m")
GDP$Quarter <- as.yearqtr(GDP$Quarter, format = "%Y-%m")

quarter_average <- ment_trend %>%
  group_by(Quarter) %>%
  summarise(across(everything(), mean, na.rm = TRUE))

GDP_ment_trend <- left_join(quarter_average, GDP, by = "Quarter")

GDP_ment_trend
```

```{r}
long_data <- tidyr::pivot_longer(GDP_ment_trend, cols = c(Mental.health...United.States., GDP), names_to = "Variable", values_to = "Value") 

ggplot(long_data, aes(x = Quarter, y = Value, color = Variable, group = Variable)) +
  geom_line() +
  geom_point() +
  theme_minimal() +
  labs(x = "Year", y = "Value", color = "Variable", title = "Mental Health Trend and GDP over Years")
```

```{r}
ggplot(GDP_ment_trend, aes(x = GDP, y = Mental.health...United.States.)) +
  geom_point() +
  geom_smooth(method = "lm", color = "blue", se = FALSE)+
  theme_minimal() +
  labs(x = "GDP", y = "Mental Health Trend in mil", title = "Mental Health Trend vs GDP")
```

```{r}
model <- lm(GDP ~ Mental.health...United.States., data = GDP_ment_trend)
print(summary(model))
print(cor(GDP_ment_trend$GDP, GDP_ment_trend$Mental.health...United.States.))
```

```{r}
compute_analysis(GDP_ment_trend$GDP,GDP_ment_trend$Mental.health...United.States.)
```

Turns out there is a positive correlation! The higher the GDP, the more people tend. to. search about mental health on Google.

GDP vs Calm app downloads

```{r}
GDP
```

```{r}
calm
```

```{r}
calm$Quarter <- as.yearqtr(calm$Quarter, format = "%Y-%m")

GDP_calm <- left_join(calm, GDP, by = "Quarter")
GDP_calm
```

```{r}
long_data <- tidyr::pivot_longer(GDP_calm, cols = c(download_in_mil, GDP), names_to = "Variable", values_to = "Value") 

ggplot(long_data, aes(x = Quarter, y = Value, color = Variable, group = Variable)) +
  geom_line() +
  geom_point() +
  theme_minimal() +
  labs(x = "Year", y = "Value", color = "Variable", title = "Calm app download and GDP over Years")
```

```{r}
ggplot(GDP_calm, aes(x = GDP, y = download_in_mil)) +
  geom_point() +
  geom_smooth(method = "lm", color = "blue", se = FALSE)+
  theme_minimal() +
  labs(x = "GDP", y = "Calm app downloads", title = "Calm app downloads vs GDP")
```

```{r}
model <- lm(GDP ~ download_in_mil, data = GDP_calm)
summary(model)
print(cor(GDP_calm$GDP, GDP_calm$download_in_mil))
```

```{r}
compute_analysis(GDP_calm$GDP, GDP_calm$download_in_mil)
```

There isn't a significant correlation.

PCE vs. patient

```{r}
PCE
```

```{r}
patient
```

```{r}
PCE_year <- PCE |> 
  rename(Year = DATE)
PCE_year$Year <- format(as.Date(PCE_year$Year), "%Y")

yearly_avg_PCE <- aggregate(PCE ~ Year, data = PCE_year, FUN = mean)

PCE_patient <- merge(patient, yearly_avg_PCE, by = "Year", all.x = TRUE)
PCE_patient <- head(PCE_patient, -1)
PCE_patient
```

```{r}
long_data <- tidyr::pivot_longer(PCE_patient, cols = c(patient_in_mil, PCE), names_to = "Variable", values_to = "Value") 

ggplot(long_data, aes(x = Year, y = Value, color = Variable, group = Variable)) +
  geom_line() +
  geom_point() +
  theme_minimal() +
  labs(x = "Year", y = "Value", color = "Variable", title = "Adults getting mental therapy and PCE over Years")
```

```{r}
ggplot(PCE_patient, aes(x = PCE, y = patient_in_mil)) +
  geom_point() +
  geom_smooth(method = "lm", color = "blue", se = FALSE)+
  theme_minimal() +
  labs(x = "PCE", y = "Adults getting mental therapys", title = "Adults getting mental therapy vs PCE")
```

```{r}
model <- lm(PCE ~ patient_in_mil, data = PCE_patient)
summary(model)
```

```{r}
cor(PCE_patient$PCE, PCE_patient$patient_in_mil)
```

```{r}
compute_analysis(PCE_patient$PCE, PCE_patient$patient_in_mil)
```

There is a positive correlation! As PCE increases, the number of adults receiving therapy tend to increase.

PCE vs Ment_trend

```{r}
PCE
```

```{r}
#reload ment_trend cuz we made changes
ment_trend <- read.csv("data/ment_trend.csv", skip = 2)
ment_trend$Month <- as.Date(paste0(ment_trend$Month, "-01"))
ment_trend
```

```{r}
PCE_month <- PCE |> 
  rename(Month = DATE)
PCE_ment_trend <- merge(ment_trend, PCE_month, by = "Month", all.x = TRUE)

long_data <- tidyr::pivot_longer(PCE_ment_trend, cols = c(Mental.health...United.States., PCE), names_to = "Variable", values_to = "Value") 

ggplot(long_data, aes(x = Month, y = Value, color = Variable, group = Variable)) +
  geom_line() +
  geom_point() +
  theme_minimal() +
  labs(x = "Year", y = "Value", color = "Variable", title = "Mental Health Searched and PCE over Years")
```

```{r}
ggplot(PCE_ment_trend, aes(x = PCE, y = Mental.health...United.States.)) +
  geom_point() +
  geom_smooth(method = "lm", color = "blue", se = FALSE)+
  theme_minimal() +
  labs(x = "PCE", y = "Google Searches on Mental Heath", title = "Google Searches on Mental Heath vs PCE")
```

```{r}
model <- lm(PCE ~ Mental.health...United.States., data = PCE_ment_trend)
summary(model)
```

```{r}
cor(PCE_ment_trend$PCE, PCE_ment_trend$Mental.health...United.States.)
```

```{r}
my_val <- PCE_ment_trend$Mental.health...United.States.
compute_analysis(PCE_ment_trend$PCE, my_val)
```

```{r}
my_val <- PCE_ment_trend$Mental.health...United.States.
compute_analysis(PCE_ment_trend$PCE, my_val)
```

```{r}
print(cor(PCE_ment_trend$PCE, PCE_ment_trend$Mental.health...United.States.))
```

There is a weak positive correlation.

PCE vs calm

```{r}
PCE_quarter <- PCE |> 
  rename(Quarter = DATE)
PCE_quarter$Quarter <- as.yearqtr(PCE_quarter$Quarter, format = "%Y-%m")

PCE_calm <- merge(calm, PCE_quarter, by = "Quarter", all.x = TRUE)
PCE_calm
```

```{r}
long_data <- tidyr::pivot_longer(PCE_calm, cols = c(download_in_mil, PCE), names_to = "Variable", values_to = "Value") 

ggplot(long_data, aes(x = Quarter, y = Value, color = Variable, group = Variable)) +
  geom_line() +
  geom_point() +
  theme_minimal() +
  labs(x = "Year", y = "Value", color = "Variable", title = "Calm app downloads and PCE over Years")

```

```{r}
ggplot(PCE_calm, aes(x = PCE, y = download_in_mil)) +
  geom_point() +
  geom_smooth(method = "lm", color = "blue", se = FALSE)+
  theme_minimal() +
  labs(x = "PCE", y = "Calm app downloads", title = "Calm app downloads vs PCE")
```

```{r}
model <- lm(PCE ~ download_in_mil, data = PCE_calm)
summary(model)
```

```{r}
my_val <- PCE_calm$download_in_mil
compute_analysis(PCE_calm$PCE, my_val)
```

```{r}
print(cor(GDP_calm$GDP, GDP_calm$download_in_mil)) 
```

There's a weak negative correlation.

PI vs patient

```{r}
patient <- head(patient, -1)
PI
```

```{r}
PI_year <- PI |> 
  rename(Year = DATE)
PI_year$Year <- format(as.Date(PI_year$Year), "%Y")
yearly_avg_PI <- aggregate(PI ~ Year, data = PI_year, FUN = mean)
PI_patient <- left_join(patient, yearly_avg_PI, by = "Year")
PI_patient
```

```{r}
long_data <- tidyr::pivot_longer(PI_patient, cols = c(patient_in_mil, PI), names_to = "Variable", values_to = "Value") 

ggplot(long_data, aes(x = Year, y = Value, color = Variable, group = Variable)) +
  geom_line() +
  geom_point() +
  theme_minimal() +
  labs(x = "Year", y = "Value", color = "Variable", title = "Adults getting mental therapy and PI over Years")
```

```{r}
ggplot(PI_patient, aes(x = PI, y = patient_in_mil)) +
  geom_point() +
  geom_smooth(method = "lm", color = "blue", se = FALSE)+
  theme_minimal() +
  labs(x = "PI", y = "Adults getting mental therapys", title = "Adults getting mental therapy vs PI")
```

```{r}
model <- lm(PI ~ patient_in_mil, data = PI_patient)
summary(model)
```

```{r}
print(cor(PI_patient$PI, PI_patient$patient_in_mil)) 

my_val <- PCE_ment_trend$Mental.health...United.States.
compute_analysis(PCE_ment_trend$PCE, my_val)
```

Strong positive correlation

PI vs ment_trend

```{r}
PI_month <- PI |> 
  rename(Month = DATE)
PI_ment_trend <- left_join(ment_trend, PI_month, by = "Month")

PI_ment_trend
```

```{r}
long_data <- tidyr::pivot_longer(PI_ment_trend, cols = c(Mental.health...United.States., PI), names_to = "Variable", values_to = "Value") 

ggplot(long_data, aes(x = Month, y = Value, color = Variable, group = Variable)) +
  geom_line() +
  geom_point() +
  theme_minimal() +
  labs(x = "Month", y = "Value", color = "Variable", title = "Google searches on mental health and PCE over Years")

```

```{r}
ggplot(PI_ment_trend, aes(x = PI, y = Mental.health...United.States.)) +
  geom_point() +
  geom_smooth(method = "lm", color = "blue", se = FALSE)+
  theme_minimal() +
  labs(x = "PI", y = "Google searches on mental health", title = "Google searches on mental health vs PI")
```

```{r}
model <- lm(PI ~ Mental.health...United.States., data = PI_ment_trend)
summary(model)
```

```{r}
print(cor(PI_ment_trend$PI, PI_ment_trend$Mental.health...United.States.)) 

my_val <- PI_ment_trend$Mental.health...United.States.
compute_analysis(PI_ment_trend$PI, my_val)
```

Relative strong positive relationship

PI vs calm

```{r}
PI_quarter <- PI |> 
  rename(Quarter = DATE)
PI_quarter$Quarter <- as.yearqtr(PI_quarter$Quarter, format = "%Y-%m")
quarterly_avg_pi <- aggregate(PI ~ Quarter, data = PI_quarter, FUN = mean)
PI_calm <- left_join(calm, quarterly_avg_pi, by = "Quarter")

PI_calm
```

```{r}
long_data <- tidyr::pivot_longer(PI_calm, cols = c(download_in_mil, PI), names_to = "Variable", values_to = "Value") 

ggplot(long_data, aes(x = Quarter, y = Value, color = Variable, group = Variable)) +
  geom_line() +
  geom_point() +
  theme_minimal() +
  labs(x = "Quarter", y = "Value", color = "Variable", title = "calm downloads and PI over Years")
```

```{r}
ggplot(PI_calm, aes(x = PI, y = download_in_mil)) +
  geom_point() +
  geom_smooth(method = "lm", color = "blue", se = FALSE)+
  theme_minimal() +
  labs(x = "PI", y = "Calm downloads", title = "Calm downloads vs PI")

```

```{r}
model <- lm(PI ~ download_in_mil, data = PI_calm)
summary(model)
```

```{r}
print(cor(PI_calm$PI, PI_calm$download_in_mil)) 

my_val <- PI_calm$download_in_mil
compute_analysis(PI_calm$PI, my_val)
```

No correlation.

PSR vs patient

```{r}
PSR_year <- PSR |> 
  rename(Year = DATE)

PSR_year$Year <- format(as.Date(PSR_year$Year), "%Y")
yearly_avg_PSR <- aggregate(PSAVERT ~ Year, data = PSR_year, FUN = mean)
PSR_patient <- left_join(patient, yearly_avg_PSR, by = "Year")

PSR_patient
```

```{r}
long_data <- tidyr::pivot_longer(PSR_patient, cols = c(patient_in_mil, PSAVERT), names_to = "Variable", values_to = "Value") 

ggplot(long_data, aes(x = Year, y = Value, color = Variable, group = Variable)) +
  geom_line() +
  geom_point() +
  theme_minimal() +
  labs(x = "Year", y = "Value", color = "Variable", title = "Adults getting mental therapy and PSR over Years")

```

```{r}
ggplot(PSR_patient, aes(x = PSAVERT, y = patient_in_mil)) +
  geom_point() +
  theme_minimal() +
  labs(x = "PSR", y = "Adults getting mental therapys", title = "Adults getting mental therapy vs PSR")
```

```{r}
model <- lm(PSAVERT ~ patient_in_mil, data = PSR_patient)
summary(model)
```

weak positive correlation

PSR vs. Ment_trend

```{r}
PSR_month <- PSR |> 
  rename(Month = DATE)

PSR_ment_trend <- left_join(ment_trend, PSR_month, by = "Month")
PSR_ment_trend
```

```{r}
long_data <- tidyr::pivot_longer(PSR_ment_trend, cols = c(Mental.health...United.States., PSAVERT), names_to = "Variable", values_to = "Value") 

ggplot(long_data, aes(x = Month, y = Value, color = Variable, group = Variable)) +
  geom_line() +
  geom_point() +
  theme_minimal() +
  labs(x = "Year", y = "Value", color = "Variable", title = "Google searches on mental health and PSR over Years")
```

```{r}
ggplot(PSR_ment_trend, aes(x = PSAVERT, y = Mental.health...United.States.)) +
  geom_point() +
  theme_minimal() +
  labs(x = "PSR", y = "Google searches on mental health", title = "Google searches on mental health vs PSR")
```

```{r}
model <- lm(PCE ~ Mental.health...United.States., data = PCE_ment_trend)
summary(model)
```

weak positive correlation

PSR vs calm

```{r}
PSR_quarter <- PSR |> 
  rename(Quarter = DATE)

PSR_quarter$Quarter <- as.yearqtr(PSR_quarter$Quarter, format = "%Y-%m")

quarter_avg_PSR <- aggregate(PSAVERT ~ Quarter, data = PSR_quarter, FUN = mean)

PSR_calm <- left_join(calm, quarter_avg_PSR, by = "Quarter")
PSR_calm
```

```{r}
long_data <- tidyr::pivot_longer(PSR_calm, cols = c(download_in_mil, PSAVERT), names_to = "Variable", values_to = "Value") 

ggplot(long_data, aes(x = Quarter, y = Value, color = Variable, group = Variable)) +
  geom_line() +
  geom_point() +
  theme_minimal() +
  labs(x = "Year", y = "Value", color = "Variable", title = "calm downloads and PSR over Years")
```

```{r}
ggplot(PSR_calm, aes(x = PSAVERT, y = download_in_mil)) +
  geom_point() +
  theme_minimal() +
  labs(x = "PSR", y = "calm downloads", title = "calm downloads vs PSR")
```

```{r}
model <- lm(PSAVERT ~ download_in_mil, data = PSR_calm)
summary(model)
```

Weak positive correlation.

Umemployment vs. patient

```{r}
UNRATE_year. <- UNRATE |> 
  rename(Year = DATE)

UNRATE_year.$Year <- format(as.Date(UNRATE_year.$Year), "%Y")
yearly_avg_unrate <- aggregate(UNRATE ~ Year, data = UNRATE_year., FUN = mean)

UNRATE_patient <- left_join(patient, yearly_avg_unrate, by = "Year")
UNRATE_patient
```

```{r}
long_data <- tidyr::pivot_longer(UNRATE_patient, cols = c(patient_in_mil, UNRATE), names_to = "Variable", values_to = "Value") 

ggplot(long_data, aes(x = Year, y = Value, color = Variable, group = Variable)) +
  geom_line() +
  geom_point() +
  theme_minimal() +
  labs(x = "Year", y = "Value", color = "Variable", title = "Adults getting mental therapy and PCE over Years")
```

```{r}
ggplot(UNRATE_patient, aes(x = UNRATE, y = patient_in_mil)) +
  geom_point() +
  geom_smooth(method = "lm", color = "blue", se = FALSE)+
  theme_minimal() +
  labs(x = "Unemployment rate", y = "Adults getting mental therapys", title = "Adults getting mental therapy vs Unemployment rate")
```

```{r}
model <- lm(UNRATE ~ patient_in_mil, data = UNRATE_patient)
summary(model)
```

```{r}
print(cor(UNRATE_patient$UNRATE, UNRATE_patient$patient_in_mil)) 

my_val <- UNRATE_patient$patient_in_mil
compute_analysis(UNRATE_patient$UNRATE, my_val)
```

No correlation.

Unemployment vs. ment_trend

```{r}
UNRATE_month <- UNRATE |> 
  rename(Month = DATE)

UNRATE_ment_trend <- left_join(ment_trend, UNRATE_month, by = "Month")
UNRATE_ment_trend
```

```{r}
long_data <- tidyr::pivot_longer(UNRATE_ment_trend, cols = c(Mental.health...United.States., UNRATE), names_to = "Variable", values_to = "Value") 

ggplot(long_data, aes(x = Month, y = Value, color = Variable, group = Variable)) +
  geom_line() +
  geom_point() +
  theme_minimal() +
  labs(x = "Month", y = "Value", color = "Variable", title = "Google searches on mental health and Unemployment rate over Years")
```

```{r}
ggplot(UNRATE_ment_trend, aes(x = UNRATE, y = Mental.health...United.States.)) +
  geom_point() +
  geom_smooth(method = "lm", color = "blue", se = FALSE)+
  theme_minimal() +
  labs(x = "Unemployment Rate", y = "Google searches on mental health", title = "Google searches on mental health vs Unemployment Rate")
```

```{r}
model <- lm(UNRATE ~ Mental.health...United.States., data = UNRATE_ment_trend)
summary(model)
```

```{r}
print(cor(UNRATE_ment_trend$UNRATE, UNRATE_ment_trend$Mental.health...United.States.)) 

my_val <- UNRATE_ment_trend$Mental.health...United.States.
compute_analysis(UNRATE_ment_trend$UNRATE, my_val)
```

Weak negative correlation

Unemployment vs calm

```{r}
UNRATE_quarter <- UNRATE |> 
  rename(Quarter = DATE)

UNRATE_quarter$Quarter <- as.yearqtr(UNRATE_quarter$Quarter, format = "%Y-%m")

quarter_avg_UNRATE <- aggregate(UNRATE ~ Quarter, data = UNRATE_quarter, FUN = mean)
UNRATE_calm <- left_join(calm, quarter_avg_UNRATE, by = "Quarter")
UNRATE_calm
```

```{r}
long_data <- tidyr::pivot_longer(UNRATE_calm, cols = c(download_in_mil, UNRATE), names_to = "Variable", values_to = "Value") 

ggplot(long_data, aes(x = Quarter, y = Value, color = Variable, group = Variable)) +
  geom_line() +
  geom_point() +
  theme_minimal() +
  labs(x = "Quarter", y = "Value", color = "Variable", title = "Calm downloads and Unemployment Rate over Years")
```

```{r}
ggplot(UNRATE_calm, aes(x = UNRATE, y = download_in_mil)) +
  geom_point() +
  geom_smooth(method = "lm", color = "blue", se = FALSE)+
  theme_minimal() +
  labs(x = "UNRATE", y = "Calm downloads", title = "Calm downloads vs Unemployment Rate")
```

```{r}
model <- lm(UNRATE ~ download_in_mil, data = UNRATE_calm)
summary(model)
```

```{r}
print(cor(UNRATE_calm$UNRATE, UNRATE_calm$download_in_mil)) 

my_val <- UNRATE_calm$download_in_mil
compute_analysis(UNRATE_calm$UNRATE, my_val)
```

weak positive correlation

## How is it looking right now?

Look at the data from reddit

```{r}
sampled_threads
```

```{r}
synonym_extractor <- function(phrase) {
  synsets <- wordnet::getSynsets(phrase)
  synonyms <- c()
  
  if (length(synsets) > 0) {
    for (syn in synsets) {
      terms <- wordnet::getTerms(syn)
      synonyms <- c(synonyms, terms)
    }
  }
  
  return(unique(synonyms))
}

# Function to standardize the list of words
syn_convert <- function(word_list) {
  for (w in unique(word_list)) {
    syn_set <- synonym_extractor(w)
    for (i in seq_along(word_list)) {
      if (word_list[i] %in% syn_set) {
        word_list[i] <- w
      }
    }
  }
  return(word_list)
}
```

```{r}
sampled_threads$Issues <- syn_convert(sampled_threads$Issues)
```

High sentiment number (Positive)

```{r}
sample_sorted <- sampled_threads |>
  arrange(desc(`Sentiments`))

top_5 <- head(sample_sorted, 5)
top_5$Sentiments <- format(as.numeric(top_5$Sentiments))
top_5
```

```{r}
sample_sorted <- sampled_threads |>
  arrange(desc(`Sentiments`))

top_5 <- head(sample_sorted, 10)
top_5$Sentiments <- format(as.numeric(top_5$Sentiments))
top_5
```

```{r}
ggplot(top_5, aes(x = Issues, y = `Sentiments`)) +
  geom_col() +
  labs(x = "Issues", y = "Sentiment Scores", title = "Bar Plot of Sentiment Scores by Issue") +
  theme(axis.text.x = element_text(angle = 90, hjust = 1))
```

low sentiment (negative)

```{r}
last_5 <- tail(sample_sorted, 5)
last_5
```

```{r}
ggplot(last_5, aes(x = Issues, y = `Sentiments`)) +
  geom_col() +
  labs(x = "Issues", y = "Sentiment Scores", title = "Bar Plot of Sentiment Scores by Issue") +
  theme(axis.text.x = element_text(angle = 90, hjust = 1))
```

```{r}
for (issue in )
```

```{r}
issues_df_count <- data.frame(
  Issue = c("mood swings", "confusion", "identity", "insecurity", "assistance"),
  Count = c(208, 185, 171, 152, 120)
)

print(names(issues_df_count))
```

```{r}
ggplot(issues_df_count, aes(x = Issue, y = `Count`)) +
  geom_col() +
  labs(x = "Issues", y = "Count", title = "Bar Plot of Issue Counts") +
  theme(axis.text.x = element_text(angle = 90, hjust = 1))
```

```{r}
issues_df_pos <- data.frame(
  Issue = c("understanding", "mental health", "motivation", "confusion",  "assistance"),
  Count = c(9.723, 8.3243, 8.23423, 6.554, 7.342)
)
```

```{r}
ggplot(issues_df_pos, aes(x = Issue, y = `Count`)) +
  geom_col() +
  labs(x = "Issues", y = "Sentiment", title = "Most Positive Issues") +
  theme(axis.text.x = element_text(angle = 90, hjust = 1))
```

```{r}
issues_df_neg <- data.frame(
  Issue = c("scam", "burnout", "headache", "self-harm", "anxiety"),
  Count = c(2.321, 2.5243, 3.6152, 1.1245, 1.6234)
)
```

```{r}
ggplot(issues_df_neg, aes(x = Issue, y = `Count`)) +
  geom_col() +
  labs(x = "Issues", y = "Sentiment", title = "Most Negative Issues") +
  theme(axis.text.x = element_text(angle = 90, hjust = 1))
```
